---
title: "MS_Imp_Guidelines"
output: html_document
date: '2022-07-21'
---
<!-- # Framework -->
<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards. -->

We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

## Repositories <!-- Existing ref -->
We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022]. To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022]. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].


## Software <!-- Novel ref -->

A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].


As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022]. To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:

- documented model modules [@ready4class2022];

- documented functions (including methods), written in a consistent house style [@ready4fun2022];

- citable, quality assured R packages [@ready4pack2022];

- model datasets [@ready4use2022];

- model analyses and reports [@ready4show2022]. 

The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards. However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4). Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software. Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].

```{r, child = child_docs_ls$two, echo=FALSE}
```

\blandscape

```{r, child = child_docs_ls$three, echo=FALSE}
```

\elandscape
