---
title: "MA_Results"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

```{r child="MS_Tables.Rmd", echo=FALSE}
```
```{r child="MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->

# Motivation

## Why develop OSHEMs in mental health

Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23]. The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11]. 

Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented. 

Major mental health reform programs will require the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives. Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020]. Currently, mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73]. Dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021]. These types of models could be the basis for developing reference models [@Afzali2013] intended for multiple-applications and re-use by multiple modelling teams. However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].

The development, validation and maintenance of these more complex models may be simply too onerous a burden for a single modelling team. Developing networks of modellers working on common health conditions [@Sampson2019] and collaborations across multiple modelling teams that include the ability to re-use and extend each others work, can make complex modelling projects more tractable [@Arnold2010]. Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021]. 

Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021]. Sustained long term funding is required for mental health projects to remain current and to enable the mental health modelling field address a number of key challenges. There are significant gaps in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and the theoretical basis for understanding complex mental health systems is weak [@RN2111]. Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42]. There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43]. 

Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare. Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019]. We believe greater support for open source approaches have the potential to provide more transparent, collaborative and sustained approaches to mental health system model development. 

## readyforwhatsnext
We are currently developing an open source model of the systems shaping the mental health of young people in Victoria, Australia. The model is called readyforwhatsnext and development progress is reported on a project website [@rfwn2022]. The project aims to produce a reference model that can examine multiple potential population level strategies for prevention (in 0-25 year olds) and treatment (in 12-25 year olds) of mental disorders. 

Our approach to model development is to undertake a number of discrete modelling projects and progressively link them together by means of a common framework. Sub-projects we are currently engaged in include those to develop models of people (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map health psychological measures to health utility), places (synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and platforms (representing the processes and operations of a complex primary youth mental health service). We have also previously undertaken scoping work reviewing economic evidence relating to youth mental health programs [@RN33] and plan to integrate this with the model at a future date.

# Framework
The framework we have developed consists of a set of standards and supporting toolkit for implementing open source youth mental health models.

## Standards
We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles that models are TIMELY:

 - Transparent: people can easily see how a model has been implemented and tested;
 - Iterative: a model is routinely updated to fix errors, incorporate new data and improve performance;
 - Modular: multiple models and their components can be combined to explore topics of more extensive scope;
 - Epitomized: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
 - Licensed: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
 - Yielding: a model can be deployed as an easy to use and flexible decision aid.

### Transparent Models

(a concatenation of the transparency and validity concepts defined in previous guidance [@Eddy2012])

T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories

<!-- T2 MISSING - Merged With T1 -->

T2: Models and their code and data are clearly and consistently documented

T3: Model logic is easy to follow through use of a simple and consistent syntax [abstraction and polymorphism, house style]

T4: Model analyses and reporting are implemented using a literate programming approach

<!-- T6 MISSING - Deleted -->

T5: All parts of a study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced and/or replicated by third parties using publicly available materials.

### Iterative Models
Performance - validity and usefulness

I2: Model code is version controlled

I1: Model code and data use semantic versioning

I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured

I4: Deprecation conventions are used to retire old code / data in order to minimise the risk of unintended impacts on downstream dependencies


### Modular Models

M1: Model code and data are decoupled – each is stored, managed, licensed, disseminated and cited independently

<!-- T2 MISSING - Moved to E -->

M3: Model code defines encapsulating data structures [that can be safely combined]. 



### Epitomised Models
M2: Model code is distributed as code-libraries [compare to analysis and reporting]

E2: Model code defines inheriting data-structures. 

E1: Model code deploys a combination of object oriented and functional programming.

### Licensed Models
copyleft licensing [@copyleft2022] is used to ensure that 
L1: Model code and data are available for viewing and re-use in open access online repositories under copyleft licensing arrangements.


### Yielding Models
Shiny tutorial [@SmithR2020]
Y1: Non- technical users can configure and run models via simple user-interfaces


## Toolkits

### Technical platforms

### Software Development Kit

## Application

Worked example